An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-18 Report/paper.tex
last hands

\subsubsection{Contour removal}
The contouring algorithm can create incorrect contours because of left-over noise in the image.
The tool we will use to remove these contours is a bounding box drawn around the contour.
This bounding box is the smallest rectangle containing the contour, it allows us to easily compare positions of contours in the text image.

Firstly we remove the contours of which the bounding box is inside the box of another contour.
This is possible as text segmentation returns the word in the image contained by its biggest bounding box. 
Secondly we remove contours that are too small to contain possible word parts. These contours consist of noise and punctuation.
These contours are neglected by taking the average height of all the found contours in the text.
We remove all of the contours with a height smaller than $average height * (2/3)$.

\begin{algorithm}[tb]
    \caption{Contour combination algorithm}
    \label{alg:overlap}
\begin{algorithmic}
    \STATE {\bfseries Input:}  $contour1$, $contour2$, $text$
    \STATE $xGap =$ calculateXaxisDistance $contour1$, $contour2$
    \STATE $yOverlap =$ calculateYoverlap $contour1$, $contour2$
    \STATE $avgWidth =$ getAverageWordWith $text$
    \IF{ 
    $xGap < avgWidth * (1 / 8 * 2)$ \\  {\bfseries and} \\ $yOverlap > min(contour1.height, contour2.height) / 2 $ 
    }
    \STATE combineContours $contour1$ $contour2$
    \ENDIF
\end{algorithmic}
\end{algorithm}

\subsubsection{Contour combination}
The leftover contours are used to to reconstruct the original words from the text.
This is done by combining multiple contours which consist of parts of words belonging to the same word. 
We have created an algorithm \ref{alg:overlap} that decides when to combine two word segments into a single word.

@@

\subsection{Preprocessing}
We resize the image to a fixed height of 100 pixels. 
Next we binarize the image using a combination of Gaussian blur and Otsu's method. 
The binarization method is identical to \ref{sec:binartext} but included to allow segmentation of words which are not part of a text. Binarization is essential as it is necessary for skeletonization.

@@

In this section we provide techniques to verify the correctness of segmentation points.
\cite{evalsplitpoints} discusses three approaches to evaluate segmentation point correctness: rule based techniques, cost function optimization based methods and machine learning based procedures.
In this paper we discuss machine learning based approaches precedented by a few rule based techniques.
An example of applying these correction techniques to an image is shown in \ref{fig:char_segm}.

@@

First we remove segmentation points found at the start and the end of the word image.
These points can be removed without information loss, as the alphabet does not contain letters that entirely convert to a single pixel line after skeletonization.
Next consequent segmentation points are grouped. The center of these points is considered as segmentation point.
Unless if one or more of the segmentation points in the group stems from empty columns, the new segmentation point is chosen as the center of the points representing the empty columns in the word image.
Finally we aggregate groups of consequent potential segmentation points, separated by columns containing less pixels than a threshold value 3.
This remedies the segmentation of slanted lines inside characters.

@@

\subsection{Normalization}
The character normalization step consists of two parts.
Firstly the character is padded untill the height equals the width.
A precondition for the padding step is that the image is already binarized, so that we can use white borders as padding, and this will not distort the image should binarization take place in a later stage.
The image is then resized to $44px x 44px$
Secondly padding of $10px$ is added on all sides of the character image to create whitespace around the letter.
We end up with a $64px x 64px$ character image.
The extra $10px$ padding is to make sure the letters do not stick to the edges, since the Chars74K dataset we work with utilizes borders around the provided characters. Should these borders be removed in the training process however, this should be reflected in this step by ignoring this new padding.

@@

The text to word segmentation process can be improved upon and made more robust.
Advanced text segmentation approaches can be utilized to extract the text segments from documents containing images and other unwanted elements.
A comparison of different text segmentation techniques is done by \cite{textsegm}.

>>>>

\subsubsection{Contour removal}
The contouring algorithm can create incorrect contours because of left-over noise in the image.
The tool we will use to remove these contours is the bounding box drawn around the contours.
This bounding box is the smallest rectangle containing the contour. It allows us to easily compare positions of contours in the text image.

Firstly we remove the contours of which the bounding box is inside the box of another contour.
This is possible as text segmentation returns the word in the image contained by its biggest bounding box.

Secondly we remove contours that are too small to contain possible word parts. These contours consist of noise and punctuation.
These contours are neglected by taking the average height of all the found contours in the text.
We remove all of the contours with a height smaller than $average height * (2/3)$.

\begin{algorithm}[tb]
    \caption{Contour combination algorithm}
    \label{alg:overlap}
\begin{algorithmic}
    \STATE {\bfseries Input:}  $contour1$, $contour2$, $text$
    \STATE $xGap =$ calculateXaxisDistance $contour1$, $contour2$
    \STATE $yOverlap =$ calculateYoverlap $contour1$, $contour2$
    \STATE $avgWidth =$ getAverageWordWith $text$
    \STATE $avgWordCharCount = 8$
    \IF{ 
    $xGap < avgWidth * (1 / avgWordCharCount * 2)$ \\  {\bfseries and} \\ $yOverlap > min(contour1.height, contour2.height) / 2 $ 
    }

    \STATE combineContours $contour1$ $contour2$
    \ENDIF
\end{algorithmic}
\end{algorithm}

\subsubsection{Contour combination}
The leftover contours are used to to reconstruct the original words from the text.
This is done by combining multiple contours which consist of parts of words belonging to the same word. 
For this task we have created Algorithm \ref{alg:overlap}, which decides when to combine two word segments into a single word.

@@

\subsection{Preprocessing}
We resize the image to a fixed height of 100 pixels. 
Next we binarize the image using a combination of Gaussian blur and Otsu's method. 
The binarization method is identical to \ref{sec:binartext} but included to allow segmentation of words which are not part of a text. Binarization of the word image is essential because the skeletonization algorithm requires a binary image as input.

@@

In this section we provide techniques to verify the correctness of segmentation points.
\cite{evalsplitpoints} discusses three approaches to evaluate segmentation point correctness: rule based techniques, cost function optimization based methods and machine learning based procedures.
In this paper we discuss machine learning based approaches precedented by a few rule based techniques.
An example of applying these correction techniques to an image is shown in Figure \ref{fig:char_segm}.

@@

First we remove segmentation points found at the start and the end of the word image.
These points can be removed without information loss, as the alphabet does not contain letters that entirely convert to a single pixel line after skeletonization.
Next consequent segmentation points are grouped. The center of these points is considered as segmentation point.
Unless if one or more of the segmentation points in the group stems from empty columns, the new segmentation point is chosen as the center of the points representing the empty columns in the word image.
Finally we aggregate groups of consequent potential segmentation points, separated by columns containing less pixels than a threshold value of 3.
This remedies the segmentation of slanted lines inside characters.

@@

@@

The text to word segmentation process can be improved upon and made more robust.
Advanced text segmentation approaches can be utilized to extract the text segments from documents containing images and other unwanted elements.
fA comparison of different text segmentation techniques is done by \cite{textsegm}.
